Proposed Solution

### 2017-01-22 CAV17/secs/arch.tex
nit change wording and clarify terminology

\para{Post Analysis.}
Finally, the intermediate representation generated by the learner is
analyzed to further refine the rules. One natural transformation
presented in the paper is to interpret generated (option, relation, option)
rules as the edges of a graph. We analyze the properties of this graph to
construct an ordering of rules by their importance in the system being
configured, as well as to produce a measure of complexity for any configuration
of the target system. Note that particular metrics developed in this paper are
not exhaustive. We believe the information contained in the intermediate
representation, unavailable to previous neural-network based techniques,
to contain vast potential for further inquiry.

>>>>

\para{Post Analysis.}
Finally, the intermediate representation generated by the learner is
analyzed to further refine the rules. One transformation
presented in the paper is to interpret generated
(keyword, relation, keyword) % TODO: replace with formal keyword def'n
rules as the edges of a graph. We analyze the properties of this graph to
construct an ordering of rules by their importance in the system being
configured, as well as to produce a measure of complexity for any configuration
of the target system. Note that particular metrics developed in this paper are
not exhaustive. We believe the information contained in the intermediate
representation, unavailable to neural-network based techniques,
contains vast potential for further inquiry.
